Why robot programming is hard

### 2014-08-18 paper.tex
Started adding some refs

% vim: set lbr:
\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{changebar}

@@

Yet the holy grail of personal service robots remains elusive. I believe there are three main reasons. There is a wide variety of tasks that people want service robots to perform, ranging from folding laundry, to finding lost car keys, to picking up the kids' toys, or doing the dishes and putting them away. These tasks must be performed in a variety of environments, including cluttered homes and kitchens with different affordances such as modern drawer pulls or faucet handles. Most importantly, the robots themselves must be easy to operate by non-technical people.

@@

Concurrent programming is notoriously difficult even for professional programmers due to the possibility for race conditions and the complexity of reasoning about what the program does. Professional programmers learn to use advanced techniques such as multi-threading, event-driven callbacks, and coroutines in order to specify concurrent behavior in programs. Yet these concepts are notoriously difficult to use and debug, even for trained programmers; how can we expect non-technical users to be able to do the same?

In addition to the low level concurrency needed to control multiple robot parts, there is also a need to specify concurrent robot behavior at a higher level. For example, a user may want to give the robot background tasks (such as cleaning or plugging oneself in when the battery is low) which should be scheduled in concert with foreground tasks (such as fetching a drink).

@@

Another challenge that robot programmers face is specifying how a robot should behave in an uncertain world. The world is constantly changing: any model that a robot could build of where things are located will be obsolete by the time it turns around. People walk around, objects get lost, furniture gets moved. Moreover, limitations in current sensing technology make it difficult to build a perfectly accurate model of the world. For example, differences in lighting make the same object look very different to an RGB camera. Therefore a robot cannot necessarily trust what it perceives, and it must be able to deal with the possibility that what it thinks is true is not actually true.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models and craft fault-tolerant code with frequent error checking, which seems like too much to ask of casual programmers who just want a robot to do something useful in the home.

@@

Endowing computers with common sense is still an active research area. Techniques for making use of common sense reasoning have not yet made it into the vocabulary of professional programmers. Yet these concepts will be taken for granted by end users of robots, who will expect their robots to obey common social norms as they perform their tasks.

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{changebar}

@@

Yet the holy grail of personal service robots remains elusive. I believe there are three main reasons. First, there is a wide variety of tasks that people want service robots to perform, ranging from folding laundry, to finding lost car keys, to picking up the kids' toys, or doing the dishes and putting them away. Second, these tasks must be performed in a variety of environments, including cluttered homes and kitchens with different affordances such as modern drawer pulls or faucet handles. Finally and most importantly, the robots themselves must be easy to operate by non-technical people.

@@

Concurrent programming is notoriously difficult even for professional programmers due to the possibility for race conditions and the complexity of reasoning about what the program does~\cite{shavit-cacm11}. Professional programmers learn to use advanced techniques such as multi-threading, event-driven callbacks, and coroutines in order to specify concurrent behavior in programs. Yet these concepts are notoriously difficult to use and debug, even for trained programmers; how can we expect non-technical users to be able to do the same?

In addition to the low level concurrency needed to control multiple robot parts, there is also a need to specify concurrent robot behavior at a higher level~\cite{cakmak-hri13}. For example, a user may want to give the robot background tasks (such as cleaning or plugging oneself in when the battery is low) which should be scheduled in concert with foreground tasks (such as fetching a drink).

@@

Another challenge that robot programmers face is specifying how a robot should behave in an uncertain world. The world is constantly changing: any model that a robot could build of where things are located will be obsolete by the time it turns around~\cite{fox-jair99}. People walk around, objects get lost, furniture gets moved. Moreover, limitations in current sensing technology make it difficult to build a perfectly accurate model of the world~\cite{kemp-ieee07}. For example, differences in lighting make the same object look very different to an RGB camera. Therefore a robot cannot necessarily trust what it perceives, and it must be able to deal with the possibility that what it thinks is true is not actually true.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models~\cite{darwiche-cacm10} and craft fault-tolerant code~\cite{wright-cacm09} with frequent error checking, which seems like too much to ask of casual programmers who just want a robot to do something useful in the home.

@@

Endowing computers with common sense is still an active research area~\cite{mueller-cacm09}. Techniques for making use of common sense reasoning have not yet made it into the vocabulary of professional programmers. Yet these concepts will be taken for granted by end users of robots, who will expect their robots to obey common social norms as they perform their tasks.
